\huge Tor's Usability for Censorship Circumvention

### 2016-04-25 pets2017-paper/pets2017-paper.tex
nathan's suggestions.

  \begin{abstract}
{Tor has grown beyond its original purpose as an anonymity tool and has 
become a widely-used censorship circumvention tool.
This is the first study to examine Tor's usability as a censorship circumvention tool.
We evaluate, redesign, and test the Tor configuration interface by
placing users in simulated censorship environments, instruct them to use Tor
to circumvent censorship, and measuring their interactions with the interface.
A 16-participant qualitative user study identifies common user struggles while circumventing censorship.
We use the results as feedback to redesign the configuration interface.
A 124-participant quantitative user study tests the impact of our changes
to find that our changes results in a significant reduction 
in the spent configuring a connection, while maintaining the same rate of success. We
conclude with recommendations for changes to the current configuration interface and discuss
alternative configuration processes with different balances of risk, automation, and user input.}
\end{abstract}
  \keywords{User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

Tor is an anonymity network that routes traffic through a series of relays
that makes it difficult to observe the source and destination~\cite{dingledine2004tor}. Tor's anonymizing functionality coincidentally also circumvented censorship. Eventually, censorship circumvention became a common enough use case for Tor that many countries attempt to block Tor for that reason~\cite{winter2012great}. Today, Tor explicitly provides support for censorship circumvention through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network indistinguishable, and advanced techniques to resist blocking.

This is the first user study investigating the usability of Tor as a censorship circumvention tool. Our experiments are both a case study of observing users circumvent censorship, and a step toward helping current Tor users by making censorship circumvention easier. All Tor users will benefit from improving the configuration interface, and therefore increasing the adoption of Tor as a censorship circumvention tool. Users who successfully use Tor to circumvent censorship will be provided with extra security features that other censorship circumvention tools do not provide, while users who use Tor as an anonymity system benefit from an increased the number of overall users on the Tor network~\cite{dingledine2006anonymity}.

We evaluate, redesign, and test the Tor configuration interface by
measuring participants' interactions with the interface in various censorship environments.
The first user study is a small-scale, one-on-one experiment that collected 
behavioral patterns and failure cases with the interface through user observations
and interviews (Section~\ref{sec:qualitative}). This feedback was used to make changes to the interface (Section~\ref{redesign}). The second user study is a large-scale, data-centric user study
that collected data on user interactions with the interface to quantify the impact of the design changes (Section~\ref{sec:quantitative}).

We find that users do not know if they require additional configuration to circumvent censorship, make incorrect assumptions based on interface layout, and do not know what to do in the event of a failure. We redesign the interface to build users' mental models, provide instructive text, and assist on error. These changes decreased the time participants spent configuring their connections, with no decrease in success rates. We conclude with recommendations of changes that we believe will help the most users circumvent censorship and connect to Tor.

@@

There have been been no published usability evaluations of
Tor Browser since the release of the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
The most recent usability effort is an unpublished pilot study by Lee and Fifield~\cite{uxsprint} 
that tested the downloading, installation, and browsing tasks in Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets},
some of which influenced changes in Tor Browser version~4.5 and later.

Previous user studies have been on the whole browsing experience,
without focusing on specific features in isolation.
We choose to focus our study on 
the browser's configuration interface, which guides users through setting up network components required to circumvent censorship. 
This study examines that interface with a focus on circumvention,
though we believe that this research and the changes we recommend
can be beneficial for non-circumventing users as well.

\section{Background}
This section talks about how the configuration interface relates to Tor, what network components are involved in censorship circumvention, and which configuration settings are required to bypass levels of Tor-adverse censorship environments.

\subsection{Tor, Tor Browser, and Tor Launcher}
The recommended way to use Tor is through Tor Browser~\cite{torbrowser},
a modified Firefox browser that includes a built-in Tor client.
Tor Browser has a software component called Tor Launcher that
starts, stops, and otherwise controls the underlying Tor processes.
Tor Launcher's graphical user interface gives access to a variety of 
sophisticated circumvention mechanisms, asking the user
to configure a proxy and bridge (if necessary) before connecting to Tor
for the first time. This is the target of our study.

In principle, the process of configuring a proxy and bridge can be automated, but
the interface eschews automatic configuration through network probing
in favor of guided manual configuration to give users agency in configuring their connection.
A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
However, this burdens the user to grapple with technical concepts such as 
bridges, pluggable transports, and proxies and to configure their connection correctly.

\subsection{Bridges, Pluggable Transports, and Proxies} 
Internet censors seek to block network resources, such as websites, through 
a variety of means, such as falsifying DNS responses, blocking IP addresses, 
filtering keywords, and detecting protocols by deep packet inspection.
Censors can block the Tor network by blocking the list of Tor relays, which 
are public. However, it becomes challenging to block access to Tor when
the Tor network is augmented with \emph{bridges} and \emph{pluggable transports}.
Fig.~\ref{fig:topology} illustrates the interacting components.

@@

Bridges are unlisted Tor relays that make it possible for a user to connect
to the Tor network even if a censor blocks all publicly listed Tor relays.
Pluggable transports are special protocols that run on bridges and obfuscate
Tor's network protocol to make it difficult to detect. 
Configuring a bridge requires providing one or more
``bridge lines,'' a specification of a bridge that
includes its IP address, transport type, and other metadata.
For ease of use, the interface has hard-coded options for 
the user to choose a group of bridges that use a particular
pluggable transport. For example, choosing  the hard-coded ``obfs3'' option
configures a handful of bridges that use obfs3 pluggable transport.
Some censors block the IP addresses of the hard-coded bridges by looking
at the source code for those addresses (except ``flashproxy'' and ``meek,'' which work differently).
If the built-in bridges do not work, a user can obtain bridge lines
through out-of-band channels, for instance by email~\cite{bridgedb}.

Fig.~\ref{fig:bridge-options} paraphrases the bridge configuration
options at the time of the study and lists the available pluggable transports.
Some transports connect directly to a static IP address,
obfuscating traffic to defeat on-the-wire identification;
they rely on the secrecy of their IP addresses for their effectiveness.
These include ``fte'' and ``fte-ipv6''~\cite{fte},
which make Tor look like another protocol such as HTTP; and
``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
which encrypt Tor to look like random noise.
Other transports work differently and do not depend on connecting to a static IP address:
``flashproxy''~\cite{flashproxy} connects through third parties' web browsers,
and the three ``meek''~\cite{fifield2015blocking} options route traffic
through content delivery networks.

\begin{figure}
\small
\begin{itemize}
\renewcommand{\labelitemi}{$\circ$}
\item Connect with provided bridges\\
Transport type:
\begin{itemize}
\item flashproxy
\item fte
\item fte-ipv6
\item meek-amazon
\item meek-azure
\item meek-google
\item obfs3 (recommended)
\item obfs4
\item scramblesuit
\end{itemize}
\item Enter custom bridges\qquad\fbox{Help}\\
\end{itemize}
\caption{
Bridge selection options in Tor Launcher, as it appeared in Tor Browser~5.0.3.
The obscure strings under ``Transport type'' denote various
built-in circumvention technologies (``pluggable transports'').
Under ``Enter custom bridges,'' there is a space to paste in
a bridge line, obtained out of band.
The ``Help'' button displays instructions on obtaining
bridge lines.
}
\label{fig:bridge-options}
\end{figure}

In addition to Tor-specific components, a proxy may be necessary to connect 
outside the local network in certain managed networks, such as corporate or university networks.
Configuring a proxy requires providing the proxy protocol, IP address, port and additional optional
fields. There is no assistance or automation with this process. The user must locate the 
proxy information and correctly format this information into the configuration interface.

Technically the Tor client, pluggable transport bridge, and proxy are all
proxies. In this paper, ``proxy'' refers to a local, ordinary unobfuscated proxy such
as a SOCKS or HTTP proxy. An important distinction is that the local proxy lies within the 
censor's control.

\subsection{Circumventing Censorship with Tor}
There are many valid configuration settings to connect to the Tor network.
For instance, a user who does not need a bridge or proxy to circumvent censorship
can connect to Tor with a bridge and proxy, provided that they have been configured correctly. 
The minimum amount of configuration required, and therefore, the set of valid configuration settings,
vary depending on the censorship environment. At the maximum, users will need to know or find out:\\

\begin{itemize}
	\item{Whether they are censored} 
	\item{Whether the Tor network is censored by their ISP}
	\item{Which groups of hard-coded bridges work in their environment} 
	\item{If no hard-coded bridges work, how to get and enter in a custom bridge} 
	\item{Whether a proxy is required to access the Internet}
	\item{If a proxy is required, and if so, the proxy settings}
\end{itemize}

Uncensored users and users in censorship environments that do not explicitly 
block Tor do not require a bridge nor a proxy and can bypass the configuration process.
Users in censorship environments that explicitly block Tor but has not blocked the 
hard-coded bridges in the Tor Launcher source code are required to use a 
hard-coded bridge or custom bridge to connect to Tor. Users in a censorship environment that has explicitly 
blocked Tor relays and hard-coded bridges will be required to configure a meek bridge (which 
routes traffic through content delivery networks and therefore resists blocking via collateral damage) or 
configure a custom bridge to connect to Tor.

\section{Evaluation Criteria and Goals}
\label{sec:goals}
The series of user studies evaluated two versions of the Tor Launcher interface.
The first, which we have labeled ``OLD'' in figures and tables,
is the current version being distributed with Tor Browser.
The second, ``NEW,'' is the prototype we revised and redesigned
in order to provide better usability. Below are the empirical and 
heuristic evaluation criteria we use to assess the interfaces.

Our empirical evaluation criteria for the Tor Browser configuration
interface are from common metrics that measure ease of use: \\

\begin{enumerate}
    \item {\bfseries Task completion rate:} What percentage of users can successfully connect to Tor in a given condition.
    \item {\bfseries  Time to completion:} How long it takes between program startup and a successful connection to Tor.
    \item {\bfseries Active configuration time:} How much time a user spends actively configuring network components to connect to Tor. 
\end{enumerate}

A heuristic evaluation is a rule-based evaluation based on time-tested standards
in the user interface design community. We draw from Jacob Nielsen's ten heuristics~\cite{nielsen1994heuristic}
and other industry standards to form the following heuristic evaluation criteria: \\

@@

\section{Experimental Setup}
\label{sec:environments}
For our experiments, we use (modified versions of) Tor Browser~5.0.3, 
the most recent stable release at the time~\cite{torbrowser-503}.
Though there were new releases during the experiments,
we tested the same version across all participants to not introduce
confounding factors.

@@

\item[E2: Intermediate censorship]
The E2 environment blocks websites as in E1;
and additionally blocks the IP addresses of public Tor relays
and directory authorities, simulating a censor that knows
about circumvention and tries to stop it.
In this environment, simply clicking ``Connect'' will not work;
participants had at least to select a built-in bridge
(any type other than ``flashproxy'' would work).
A custom bridge would work but was not necessary.
% (Representative of countries such as Tunisia.)

@@

We ran a qualitative, exploratory user study to gain an 
understanding of how users interact with the configuration interface and
what common problems may be. We did this by observing participants using 
the interface to circumvent censorship, and interviewing them about
their experience.  Our observations during this study guided us in
redesigning interface and provided hypotheses to test in our quantitative study.

@@

We recruited our users from Craigslist, vaguely stating that we wanted to evaluate some piece of software. 
The recruitment text can be found in Appendix~\ref{qualitative-recruitment}. The recruitment posting contained a 
SurveyGizmo online survey that collected their demographics, technical expertise, and familiarity with Tor.
The complete prescreening survey can be found in Appendix~\ref{qualitative-prescreening}.  
We selected participants to have at least one person who has never heard of Tor, 
at least one person who has only heard of Tor, and exactly one person who has previously used Tor in each
censorship environment. We tried to evenly distribute any participants who had technical
expertise or used particular security tools throughout the censorship environments.

@@

\subsection{Procedure}
The one-hour, single-participant procedure begins when a participant enters a small 
room with a single computer, which is equipped with Tor, Chrome, Firefox, Internet Explorer, and VLC.
Each participant is informed of the risks and purpose of the study.
A researcher reads a script that informs the participant of the simulated censorship environment and
instructs them to visit sample blocked and unblocked websites
in a standard browser, to show what it looks like when a site is blocked (Appendix~\ref{qualitative-script}).
Then, the participant is asked to  complete a worksheet that gives information
on their censorship environment and instructs them
to visit one blocked website and one non-blocked website (Appendix~\ref{participant-worksheet}).
The worksheet informs the participant that the network is censored,
but does not give details of what services and websites are specifically blocked.
Participants were able to visit the unblocked website using any familiar browser,
but had to configure Tor Browser in order to visit the blocked website.

For the blocked website, we used the main page of Wikipedia,
and for the unblocked site we used the CNN homepage.
We chose these two sites because of their likely familiarity to web users;
our goal was to evaluate the user interface, not to test users with a browsing task.
After giving the instructions, the researchers stepped out of the room so that there was no interaction
between the participant and researcher for the rest of the session.
Researchers watched a live video of each participant's screen from another room
and saved the videos for review; the resulting videos and summaries
are available from our project page.
Participants had an average of 45 minutes to complete their worksheet.

We refreshed a list of Tor relay IP addresses and added them
to a firewall blacklist before each session.
In this first study, we neglected to block the IP addresses
of the Tor directory authorities, which are the first hosts
a client contacts when initiating a non-bridge connection.
This, combined with new relays appearing in the network on an hourly basis,
enabled a small number of participants to succeed with
a direct connection when we expected them to fail.
We fixed this problem in our second study by blocking the directory authorities.

After participants completed the browsing tasks or ran out of time,
we interviewed them about their experience,
taking notes of the questions and answers.
We asked three standard questions asking about their general experience, 
confusing interface features, and soliciting feedback for improvements. We followed up
with specific per-participant questions prompted from watching their screen. 
This was to verify any hypotheses we had (e.g. ``they did not know what to do on window~3'').
We paid each participant~\$30 for their time.

@@

\noindent {\bfseries Challenge 3: Users did not know how to choose which bridge and pluggable transport.}
On the bridge configuration screen, participants were intimidated by the names of the bridge transports. The most common behavior was to configure with the recommended bridge option (obfs3). If the recommended one did not work, participants did not know how to choose another.

@@

\noindent {\bfseries Challenge 4: Users do not know when they are wrong.} 
Unfortunately, many mistakes did not result in error messages, bu warnings that went unnoticed.
When participants did encounter an error message, they did not understand what errors meant (Fig.~\ref{fig:error}).\\

\noindent {\bfseries Challenge 5: Users assume they are wrong when they are right.}
If users chose particular wrong configurations (i.e. a syntactically valid but nonfunctional proxy), they would be waiting for an indefinite period of time. 
\pquote{P16}{There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.}

The progress bar also has a bug that causes it to update itself only when the level of progress increases.
If progress bar reaches a 90\% and fails, the next attempt will apparently have regressed to 0\% and remain there until the progress reaches >90\%. Due to this, participants assumed that their subsequent attempts were wrong, even if they were correct.
\pquote{P1}{It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.}

\noindent {\bfseries Challenge 6: Users assume that proxy is required after a failed connection.} 
All of our participants who failed to connect (5 of 16) failed for this reason. Many mistakenly assumed that they needed a proxy upon failure, because the interface passively redirects to the proxy screen (the last screen) after failure.

@@

From interviewing our participants, we found that these challenges result because users are not familiar with technical or Tor-specific terms, feedback on progress or an errors were inconsistent, and the interface did not instruct users on what to do in the event of a failure.

@@

From the result of our qualitative user study, we see that many users struggle with the configuration process. 
The Tor Browser configuration interface does not adequately meet our criteria from Section~\ref{sec:goals} of
managing errors gracefully, communicating in understandable language, and giving  users feedback on system state. 
We rate the severity of each issue by its frequency, impact, and persistence~\cite{nielsen1994heuristic}:\\

\begin{itemize}
\item {\bfseries Major Problem:} Error messages do not express errors in plain language nor offer solutions. 
\item {\bfseries Major Problem:} The concepts mentioned in the interface and the questions that users were required to answer were too technical for the average user. 
\item {\bfseries Minor Problem:} The configuration is not visible to the users before they attempt to connect to the Tor network or while they are connecting to the Tor network.
 \end{itemize}

@@

To address these three aforementioned user interaction problems, we made the following three changes to the configuration interface:  \\

@@

\begin{enumerate}
\setcounter{enumi}{3}
\item {\bfseries Added guidance on choosing connect versus configure.} We labeled the configure option specifically for user in heavily censored situations, to urge users to not assume that a website censorship necessitates configuration.
\item {\bfseries Added explicit advice on choosing bridge transports.} The recommended bridge type is still obfs3. We added text that advises users to try a meek bridge if obfs3 does not work.

@@

\item {\bfseries Switched ordering to configure proxies first.} To build users' mental models, network components are now configured in a topologically sequential order, resembling Fig.~\ref{fig:topology} and the new progress screen. Previously, proxies were put after bridge configuration because only a small fraction of users require proxies. With auto-detection, configuring a proxy before a bridge burden users less than before.
\item {\bfseries Added clear feedback to the progress bar.} We switched the continuous progress bar to a discrete checkpoint-based progress indicator that shows the network components involved in connecting to the Tor network. This aligns with the mental model we are trying to build in the user. As connections are made with each component, the progress bar displays a green check, giving immediate feedback to the user. For instance, a user can can now see that the bridge was configured correctly, and they just need to wait to connect to the Tor network. Upon failure, users can see which components have succeeded and which have failed.
\end{enumerate}

@@

\subsection{Recruitment}
We recruited 124 participants, about 20 for each
of the six combinations of censorship environment
and interface revision.
Data analysis considerations deem 20 participants per combination a 
minimum to assume normal distributions, and 60 participants
per interface revision is adequate to have a meaningful effect size.

@@

\subsection{Discussion} 
This section talks about general trends in user behavior, common failure cases, and our recommendations for 
improving the Tor configuration interface.

>>>>

  \begin{abstract}
{Tor has grown beyond its original purpose as an anonymity tool and has 
become a widely-used censorship circumvention tool.
This is the first study to examine Tor's usability in this role.
We evaluate, redesign, and test the Tor configuration interface by
placing users in simulated censorship environments, instructed them to use Tor
to circumvent censorship, and measuring their interactions with the interface.
A 16-participant qualitative user study identifies common user struggles while circumventing censorship.
We use the results as feedback to redesign the configuration interface.
A 116-participant quantitative user study tests the impact of our changes.
We find that our changes results in a significant reduction 
in the time spent configuring a connection, while maintaining the same rate of success. We
conclude with recommendations for changes to the current configuration interface and discuss
alternative configuration processes with different balances of risk, automation, and user input.}
\end{abstract}
  \keywords{User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

Tor is an anonymity network that routes traffic through a series of relays
that make it difficult to observe the source and destination~\cite{dingledine2004tor}. Tor's anonymizing functionality also circumvented censorship. Censorship circumvention became a common enough use case for Tor that many countries attempt to block Tor for this reason~\cite{winter2012great}. Today, Tor explicitly provides support for censorship circumvention through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network less obvious, and advanced techniques to resist blocking.

This is the first user study investigating the usability of Tor as a censorship circumvention tool. Our experiments are both a case study observing users circumvent censorship and a step toward helping current Tor users by making censorship circumvention easier. All Tor users will benefit from improving the configuration interface, therefore increasing the adoption of Tor as a censorship circumvention tool. Users who successfully use Tor to circumvent censorship will be provided with extra security features that other censorship circumvention tools do not provide, while users who use Tor as an anonymity system benefit from an increased number of overall users on the Tor network~\cite{dingledine2006anonymity}.

We evaluate, redesign, and test the Tor configuration interface by
measuring participants' interactions with the interface in various censorship environments.
The first user study is a small-scale, one-on-one experiment that collected 
behavioral patterns and failure cases with the interface through user observations
and interviews (Section~\ref{sec:qualitative}). This feedback was used to make changes to the interface (Section~\ref{redesign}). The second user study is a large-scale, many-to-one experiment
that collected data on user interactions with the interface to quantify the impact of the design changes (Section~\ref{sec:quantitative}).

We find that users do not know if they require additional configuration to circumvent censorship, make incorrect assumptions based on interface layout, and do not know what to do in the event of a failure. We redesign the interface to build users' mental models, make the text easier to understand, and provide messages to assist users on error. Our changes decreased the time participants spent configuring their connections, but there was no difference in success rates. We expected the success rate to increase after providing suggestions on what to do next with error messages, but this had no effect since only 1 of 116 users encountered an error message. We conclude with recommendations of changes that we believe will help the most users circumvent censorship and connect to Tor.

@@

There have been been no published usability evaluations of
Tor Browser since the release of the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
The most recent effort is an unpublished pilot study by Lee and Fifield~\cite{uxsprint} 
that tested the downloading, installation, and browsing tasks in Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets},
some of which influenced changes in Tor Browser version~4.5 and later.

Previous user studies have been on the whole browsing experience,
without focusing on specific features in isolation.
We focus our study on 
the browser's configuration interface, which guides users through setting up network components required to circumvent censorship.

\section{Background}
This section discusses the configuration interface relates to Tor, what network components that are involved in censorship circumvention, and which configuration settings are required to bypass levels of Tor-adverse censorship environments.

\subsection{Tor, Tor Browser, and Tor Launcher}
The recommended way to use Tor is through Tor Browser~\cite{torbrowser},
a modified Firefox browser that includes a built-in Tor client.
Tor Browser has a software component called Tor Launcher that
starts, stops, and otherwise controls the underlying Tor processes.
Tor Launcher's graphical user interface gives access to a variety of 
sophisticated circumvention mechanisms, asking the user
to configure a proxy and bridge (if necessary) before connecting to Tor
for the first time. This is the object of our study.

In principle, the process of configuring a proxy and bridge can be automated, but
the interface eschews automatic configuration through network probing
in favor of guided manual configuration to give users agency in configuring their connection.
A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
However, this requires the user to grapple with technical concepts such as 
bridges, pluggable transports, and proxies.

\subsection{Bridges, Pluggable Transports, and Proxies} 
Internet censors seek to block network resources through 
a variety of means, such as falsifying DNS responses, blocking IP addresses, 
filtering keywords, and detecting protocols by deep packet inspection.
Censors can block the Tor network by blocking the list of Tor relays, which 
are public. However, it becomes challenging to block access to Tor when
the Tor network is augmented with \emph{bridges} and \emph{pluggable transports}.
Fig.~\ref{fig:topology} illustrates the interacting components.

@@

Bridges are unlisted Tor relays that make it possible for a user to connect
to the Tor network even if a censor blocks all publicly listed Tor relays.
Pluggable transports are special protocols that run on bridges and obfuscate
Tor's network protocol to make it difficult to detect. 
Configuring a bridge requires providing one or more
``bridge lines,'' a specification of a bridge that
includes its IP address, transport type, and other metadata.
For ease of use, the interface has hard-coded options for 
the user to choose a group of bridges that use a particular
pluggable transport. For example, choosing  the hard-coded obfs3 option
configures a handful of bridges that use obfs3 pluggable transport.
Some censors block the IP addresses of the hard-coded bridges by looking
at the source code for those addresses (except flashproxy and meek).
If the built-in bridges do not work, a user can obtain bridge lines
through out-of-band channels, for instance by email~\cite{bridgedb}.
Fig.~\ref{fig:bridge-options} paraphrases the bridge configuration
options at the time of the study and lists the available pluggable transports.
%Some transports connect directly to a static IP address,
%obfuscating traffic to defeat on-the-wire identification;
%they rely on the secrecy of their IP addresses for their effectiveness.
%These include ``fte'' and ``fte-ipv6''~\cite{fte},
%which make Tor look like another protocol such as HTTP; and
%``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
%which encrypt Tor to look like random noise.
%Other transports work differently and do not depend on connecting to a static IP address:
%``flashproxy''~\cite{flashproxy} connects through third parties' web browsers,
%and the three ``meek''~\cite{fifield2015blocking} options route traffic
%through content delivery networks.

\begin{figure}
\small
\begin{itemize}
\renewcommand{\labelitemi}{$\circ$}
\item Connect with provided bridges\\
Transport type:
\begin{itemize}
\item flashproxy
\item fte
\item fte-ipv6
\item meek-amazon
\item meek-azure
\item meek-google
\item obfs3 (recommended)
\item obfs4
\item scramblesuit
\end{itemize}
\item Enter custom bridges\qquad\fbox{Help}\\
\end{itemize}
\caption{
Bridge selection options in Tor Launcher, as it appeared in Tor Browser~5.0.3.
The options under ``Transport type'' denote various
built-in circumvention technologies (``pluggable transports'').
Under ``Enter custom bridges,'' there is a space to paste in
a bridge line, obtained out of band.
The ``Help'' button displays instructions on obtaining
bridge lines.
}
\label{fig:bridge-options}
\end{figure}

In addition to Tor-specific components, a proxy may be necessary to connect 
outside the local network in certain managed environments, such as corporate or university networks.
Configuring a proxy requires providing the proxy protocol, IP address, port, and additional optional
fields. There is no assistance or automation with this process. The user must locate the 
proxy information and correctly input this information into the configuration interface.

%Technically the Tor client, pluggable transport bridge, and proxy are all
%proxies. In this paper, ``proxy'' refers to a local, ordinary unobfuscated proxy such
%as a SOCKS or HTTP proxy. An important distinction is that the local proxy lies within the 
%censor's control.

\subsection{Circumventing Censorship with Tor}
There are many valid configuration settings to connect to the Tor network.
For instance, a user who does not need a bridge or proxy to circumvent censorship
can connect to Tor with a bridge and proxy, provided that they have been configured correctly. 
The minimum amount of configuration required, therefore, the set of valid configuration settings,
vary depending on the censorship environment. At the maximum, users will need to know or find out:\\

\begin{itemize}
	\item{Whether they are censored} 
	\item{Whether the Tor network is censored by their ISP}
	\item{Which groups of hard-coded bridges work in their environment} 
	\item{If no hard-coded bridges work, how to get and enter a custom bridge} 
	\item{Whether a proxy is required to access the Internet}
	\item{If a proxy is required, and if so, the proxy settings}
\end{itemize}

Uncensored users and users in censorship environments that do not explicitly 
block Tor do not require a bridge or a proxy and can bypass the configuration process.
Users in censorship environments that explicitly block Tor but have not blocked the 
hard-coded bridges in the Tor Launcher source code are required to use a 
hard-coded bridge or custom bridge to connect to Tor. Users in a censorship environment that has explicitly 
blocked Tor relays and hard-coded bridges will be required to configure a meek bridge (which 
routes traffic through content delivery networks and therefore resists blocking through collateral damage) or 
configure a custom bridge to connect to Tor.

\section{Evaluation Criteria and Goals}
\label{sec:goals}
The series of user studies evaluated two versions of the Tor Launcher interface.
The first, which we have labeled ``OLD'' in figures and tables,
is the current version being distributed with Tor Browser.
The second, ``NEW,'' is the prototype we designed
in order to provide better usability. Below are the empirical and 
heuristic evaluation criteria we use to assess the interfaces.

Our empirical evaluation criteria for the Tor Browser configuration
interface are based on common metrics that measure ease of use: \\

\begin{enumerate}
    \item {\bfseries Task completion rate:} What percentage of users can successfully connect to Tor in a given condition.
    \item {\bfseries  Time to completion:} How long it takes between program startup and a successful Tor bootstrap, which includes time spent searching online for help and waiting for a the connection to bootstrap.
    \item {\bfseries Active configuration time:} How much time a user spends actively configuring network components to connect to Tor, which only includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
\end{enumerate}

A heuristic evaluation is based on standards
in the user interface design community. We draw from Jacob Nielsen's ten heuristics~\cite{nielsen1994heuristic}
to form the following heuristic evaluation criteria: \\

@@

\section{Experimental Setup}
\label{sec:environments}
For our experiments, we use instrumented versions of Tor Browser~5.0.3, 
the most recent stable release at the time~\cite{torbrowser-503}.
Though there were new releases during the experiments,
we tested the same version across all participants to not introduce
confounding factors.

@@

\item[E2: Intermediate censorship]
The E2 environment blocks websites as in E1;
it additionally blocks the IP addresses of public Tor relays
and directory authorities, simulating a censor that knows
about circumvention and tries to stop it.
In this environment, simply clicking ``Connect'' will not work;
participants had to select a built-in bridge
(any type other than ``flashproxy'' would work).
A custom bridge would work but was not necessary.
% (Representative of countries such as Tunisia.)

@@

We ran a qualitative, exploratory user study to gain an 
understanding of how users interact with the configuration interface and
what common problems may be. We did this by observing participants using 
the interface to circumvent censorship and interviewing them about
their experience.  Our observations during this study guided us in
redesigning the interface and provided hypotheses to test in our quantitative study.

@@

We recruited our users from Craigslist, vaguely stating that we wanted to evaluate some piece of software. 
The recruitment text can be found in Appendix~\ref{qualitative-recruitment}. The recruitment posting contained a 
SurveyGizmo online survey that collected their demographics, technical expertise, and familiarity with Tor.
The complete prescreening survey can be found in Appendix~\ref{qualitative-prescreening}.  
We selected participants in each censorship environment to have at least one person who has never heard of Tor, 
at least one person who has only heard of Tor, and exactly one person who has previously used Tor
. We tried to evenly distribute any participants who had technical
expertise or used particular security tools throughout the censorship environments.

@@

\subsection{Procedure}
The one-hour, single-participant procedure began when a participant enters a small 
room with a single computer, which is equipped with Tor, Chrome, Firefox, Internet Explorer, and VLC.
Each participant is informed of the risks and purpose of the study.
A researcher read a script that informed the participant of the simulated censorship environment and
instruct them to visit sample blocked and unblocked websites
in a standard browser, to show what it looks like when a site is blocked (Appendix~\ref{qualitative-script}).
Then, the participant was asked to complete a worksheet that gives information
on their censorship environment and instructed them
to visit one blocked website and one non-blocked website (Appendix~\ref{participant-worksheet}).
The worksheet informed the participant that the network is censored,
but did not give details of what services and websites are specifically blocked.
Participants were able to visit the unblocked website using any familiar browser,
but had to configure Tor Browser in order to visit the blocked website.

For the blocked website, we used the main page of Wikipedia,
and for the unblocked site we used the CNN homepage.
We chose these two sites because of their likely familiarity to web users;
our goal was to evaluate the user interface, not to test users with a browsing task.
After instructions, the researchers stepped out of the room so that there was no interaction
between the participant and researcher for the rest of the session.
Researchers watched a live video of each participant's screen from another room
and saved the videos for review; the resulting videos and summaries
are available from our project page.
Participants had an average of 45 minutes to complete their worksheet.

After participants completed the browsing tasks or ran out of time,
we interviewed them about their experience,
taking notes of the questions and answers.
We asked three standard questions asking about their general experience, 
confusing interface features, and feedback for improvements. We followed up
with specific questions prompted from watching their screen. 
This was to verify any hypotheses we had (e.g. ``they did not know what to do on window~3'').
We paid each participant~\$30 for their time.

@@

\noindent {\bfseries Challenge 3: Users did not know how to choose which bridge and pluggable transport.}
On the bridge configuration screen, participants were confused by the names of the bridge transports. The most common behavior was to configure with the recommended bridge option (obfs3). If the recommended one did not work, participants did not know how to choose another.

@@

\noindent {\bfseries Challenge 4: Users do not know when they are wrong.} 
Unfortunately, many mistakes did not result in error messages, but warnings that went unnoticed.
When participants did encounter an error message, they did not understand what errors meant (Fig.~\ref{fig:error}).\\

\noindent {\bfseries Challenge 5: Users assume they are wrong when they are right.}
The progress bar has a bug that causes it to update only when the level of progress increases.
If progress bar reaches a 90\% and fails, the next attempt will apparently have regressed to 0\% and remain there until the progress reaches >90\%. Due to this, participants assumed that their subsequent attempts were wrong, even if they were correct.
\pquote{P1}{It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.}
\pquote{P16}{There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.}

\noindent {\bfseries Challenge 6: Users assume that proxy is required after a failed connection.} 
All of our participants who failed to connect (5 of 16) failed for this reason. Many mistakenly assumed that they needed a proxy upon failure, because the interface redirects to the proxy screen (the last screen) after failure.

@@

From interviewing our participants, we found that these challenges result because users are not familiar with technical or Tor-specific terms, feedback on progress or errors was inconsistent, and the interface did not instruct users on what to do in the event of a failure.

@@

From the results of our qualitative user study, we see that many users struggle with the configuration process. 
The Tor Browser configuration interface does not adequately meet our criteria from Section~\ref{sec:goals} of
managing errors gracefully, communicating in understandable language, and giving  users feedback on system state. 
We rate the severity of each issue by its frequency, impact, and persistence~\cite{nielsen1994heuristic}:\\

\begin{itemize}
\item {\bfseries Major Problem:} Error messages do not express errors in plain language nor offer solutions. 
\item {\bfseries Major Problem:} The concepts mentioned in the interface and the questions that users are required to answer are too technical for the average user. 
\item {\bfseries Minor Problem:} The configuration is not visible to the users before they attempt to connect or while they are connecting to the Tor network.
 \end{itemize}

@@

To address these problems, we made the following three changes to the configuration interface:  \\

@@

\begin{enumerate}
\setcounter{enumi}{3}
\item {\bfseries Added guidance on choosing to connect or configure.} We labeled the configure option specifically for user in heavily censored situations, to urge users to not assume that a website censorship necessitates configuration.
\item {\bfseries Added explicit advice on choosing bridge transports.} The recommended bridge type is still obfs3. We added text that advises users to try a meek bridge if obfs3 does not work.

@@

\item {\bfseries Switched ordering to configure proxies first.} To build users' mental models, network components are now configured in a topologically sequential order, resembling Fig.~\ref{fig:topology} and the new progress screen. Previously, proxies were put after bridge configuration because only a small fraction of users require proxies. With auto-detection, configuring a proxy before a bridge burdens users less than before.
\item {\bfseries Added clear feedback to the progress bar.} We switched the continuous progress bar to a discrete checkpoint-based progress indicator that shows the network components involved in connecting to the Tor network. This aligns with the mental model we are trying to build in the user. As connections are made with each component, the progress bar displays a green check, giving immediate feedback to the user. For instance, a user can can now see that the bridge was configured correctly, and they just need to wait to connect to the Tor network. Upon failure, users can see which components have succeeded and which have failed.
\end{enumerate}

@@

\subsection{Recruitment}
We recruited 124 participants, about 20 for each
condition.
Data analysis considerations deem 20 participants per combination a 
minimum to assume normal distributions, and 60 participants
per interface revision is adequate to have a meaningful effect size.

@@

\subsection{Discussion} 
This section details general trends in user behavior, common failure cases, and our recommendations for 
improving the Tor configuration interface.
